---
title: "fy20_perf_forecast"
author: "Brandon Kessler"
date: "March 28, 2019"
output: 
  html_document:
    code_folding: show
    toc: TRUE
    toc_float: TRUE
---

```{r setup, include=FALSE}
# SETUP

# Clear all variables in workspace
rm(list=ls())

# Set wd
setwd("U:/models")


# libs
library(tidyverse)
library(lubridate)

# import data
df <- read.csv('/data/forecasting/perf_forecast_dataset_clx.csv') %>%
  rename(Series = 1)

df.to_pred <- df %>%
  mutate(Month = as.factor(Month),
         composer_tier = as.factor(composer_tier),
         guest_artist_tier = as.factor(guest_artist_tier)) %>%
  select(-Series,-Date,-FY,-Goal)
```

# 10yr Regression

Through much testing, we have eliminated the following variables from the model as being statistically insignificant in predicting performance revenue:

* human name in title (ie. Joyce Yang .....)

* thanksgiving proximity (+/- one week of Thanksgiving)

* Guest conductor (it doesn't matter if it's Carl or someone else)

* guest other (have a guest artist that is not on piano or violin is irrelevent)

* the word "plays" in title (ie. Watts plays Beethoven)

* Having Beethoven, Mozart, or Tchaikovsky in the performance title

* Prior year's sub tickets sold (interestingly, last year's flex sold does matter)

* Number of words in the performance name

* Rank of composer's works (ie. Beethoven's 9th is in his top 3 works)

* Connections

This leaves us with the following regression

```{r, echo=FALSE}
# regress
df.lm <- lm(Revenue ~ .
            - human_name_in_title
            - thxgiving_prox
            - Guest_Conductor
            - guest_other
            - word_plays
            - name_Beethoven
            - name_Mozart
            - name_Tchaikovsky
            - lag_subs_1yr
            - number_of_words
            - top_3_composer_rank
            - connections,
            data = df.to_pred)
summary(df.lm)


```

Here we can see that the remaining variables are:

* Month

* Composer tier (ie. Beethoven is tier 1)

* guest_Violin (guest artist playing violin)

* guest_Piano (guest artist playing piano)

* Opera

* guest_artist_tier (this one can go either way in keeping or removing)

* prior year's flex tickets sold (the more flex tickets sold last year, the less single ticket revenue we generate this year)

Based on the R-squared, we can see that this model predicts 66% of the revenue and the remaining predictors are floating out in the world somewhere. These are likely to include things like:

* Politics

* Weather

* Social media followers/engagements

* Marketing spend

* etc...

# Model comparison

```{r, echo=FALSE}
y_pred <- as.data.frame(predict(df.lm, df.to_pred)) %>%
  rename(prediction = 1)

comparisons <- df %>%
  select(Revenue, Goal) %>%
  cbind(y_pred)

sqrt_mse_pred <- sqrt(mean((df$Revenue - y_pred$prediction)^2))
sqrt_mse_goal <- sqrt(mean((df$Revenue - df$Goal)^2))

mape_pred <- mean(abs((df$Revenue - y_pred$prediction)/df$Revenue)* 100)
mape_goal <- mean(abs((df$Revenue - df$Goal)/df$Revenue)* 100)

print(paste0('The square root of MSE for my model is ',sqrt_mse_pred,' in comparison with your methods which have a square root of MSE of ',sqrt_mse_goal,'. This indicates that my model is roughly $5000 better at predicting the revenue generated per performance.'))

```


# Re-forecasting FY20

Using my model we can re-forecast the performances for the FY20 Classics season.Below are the results:

```{r, echo=FALSE}
fy20_projections <- read.csv('/data/forecasting/projected_fy20_clx.csv') %>%
  rename(perf = 1) %>%
  select(-perf) %>%
  mutate(Month = factor(Month),
         composer_tier = factor(composer_tier),
         guest_artist_tier = factor(guest_artist_tier)) %>%
  select(-projected)

fy20_pred <- as.data.frame(predict(df.lm,fy20_projections)) %>%
  rename(prediction = 1)

fy20_comparison <- read.csv('/data/forecasting/projected_fy20_clx.csv') %>%
  rename(perf = 1) %>%
  select(perf,projected) %>%
  cbind(fy20_pred) %>%
  mutate(difference = prediction - projected)


head(fy20_comparison,nrow(fy20_comparison))
```



```{r, echo=FALSE}
library(xlsx)
write.xlsx(as.data.frame(comparisons),
           'model_forecast_comparisons.xlsx')


```