---
title: "ga_ad_spend"
output: html_document
---

```{r setup, include=FALSE}
library(ggplot2)
library(tidyverse)
library(googleAnalyticsR)
library(caTools)
library(forecast)

ga_id <- 13471302

start_date <- "1000daysAgo"
end_date <- "yesterday"
start_date2 <- "1825daysAgo"
end_date2 <- "1001daysAgo"
metrics <- c("impressions",
            "totalValue")
dimensions <- c("date")

ga_auth()

load_data <- function(ga_id,start_date,end_date,start_date2,end_date2,metrics,dimensions){
  df1 <- google_analytics(ga_id,
                          date_range = c(start_date,end_date),
                          metrics = metrics,
                          dimensions = dimensions)

  df2 <- google_analytics(ga_id,
                          date_range = c(start_date2,end_date2),
                          metrics = metrics,
                          dimensions = dimensions)
  
  df <- rbind(df1,df2)
  return(df)
}
```

## Build DF and view sample

Data is built over 5 year period and grouped by month
Total value (totalValue) represents the total revenue earned as a result of website

```{r cars}
df <- load_data(ga_id,start_date,end_date,start_date2,end_date2,metrics,dimensions) %>%
  group_by(month=floor_date(date, "month")) %>%
  summarise(totalValue=sum(totalValue),
            impressions=sum(impressions))

head(df,n=10)

```

## Summary statistics

Summary of total value and ad cost

```{r}
summary(df[,c('totalValue','impressions')])
```


## Plot data

```{r}
ggplot(df, aes(x = month)) +
  geom_line(aes(y = totalValue), color = 'dodgerblue3') +
  theme_bw()

```

## Seasonality and trend composition

```{r}
totalValue.ts <- ts(df$totalValue,
                    start = c(2014, 2),
                    end = c(2019, 2),
                    frequency = 12)
plot.ts(totalValue.ts)

ts_decomp <- stl(totalValue.ts, s.window = "period")

plot(ts_decomp)

```

## Fit with exponential triple smoothing

```{r}
fit <- ets(totalValue.ts)
plot.ts(fit$residuals)
accuracy(fit)

```

### Use the fit variable as part of the forecast function to predict future revenue
```{r}
totalValue_forecast <- forecast(fit,3)
totalValue_forecast
plot(totalValue_forecast)
```

