---
title: "ga_adWords"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
library(ggplot2)
library(tidyverse)
library(googleAnalyticsR)
library(caTools)

ga_id <- 13471302

# 5yr range
start_date <- "1825daysAgo"
end_date <- "yesterday"

metrics <- c("impressions","CPM","adClicks","CPC","totalValue","RPC","ROAS")
dimensions <- c("adGroup")

ga_auth()

load_data <- function(ga_id,start_date,end_date,metrics,dimensions){
  df <- google_analytics(ga_id,
                         date_range = c(start_date,end_date),
                         metrics = metrics,
                         dimensions = dimensions)

  return(df)
}
```

## Build DF and view sample

After building data frame, output 10 random rows to view structure of data set

```{r cars}
df <- load_data(ga_id,start_date,end_date,metrics,dimensions)
df[sample(nrow(df), 10),]

```

## View some summary statistics
```{r}
knit_print(summary(df))
```

## Set top 20 ad groups by ROAS

**ROAS - Return on Ad Spend**
This is a metric that measures the revenue from ad campaign divided by cost of ad campaign.
In other words, it measures the incremental increase in revenue from an increase in dollar spend on ads.
We are looking at this per adGroup to determine the best performing ad groups.


```{r}
top20_ROAS <- df %>%
  arrange(desc(ROAS))

top20_ROAS$adGroup <- factor(top20_ROAS$adGroup, levels = top20_ROAS$adGroup[order(top20_ROAS$ROAS)])
  
top20_ROAS <- top20_ROAS[1:20,]
top20_ROAS
```
## Plot top 20 ad groups by ROAS

```{r}

ggplot(top20_ROAS, aes(x=adGroup,y=ROAS)) +
  geom_bar(stat="identity", fill='dodgerblue2') +
  labs(title="top 20 ROAS by adGroup") + 
  theme_bw() + 
  theme(axis.text.x = element_text(angle=65, vjust=1, hjust=1))

```

## What impacts ROAS?
We can see what other independent variables impact ROAS

```{r}

# 4 months worth of data

new_start <- "120daysAgo"
m2 <- c("ROAS","newUsers","adCost")
d2 <- c('deviceCategory','date')

df2 <- load_data(ga_id,new_start,end_date,m2,d2)

levels <- unique(df2$deviceCategory)
labels <- unique(df2$deviceCategory)

df2$deviceCategory <- factor(df2$deviceCategory,
                                  levels=levels)

regressor <- lm(formula = ROAS ~ . - date, data = df2)
summary(regressor)

```